Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-09-06 paper_comparison/paper_comparison/paper_comparison.Rmd
update hypothesis testing

```{r}
mod <- poly_model(include_z = FALSE, sigma = 0.25)
dat <- mod$gen(300)
patchwork::wrap_plots(mod$plot(dat, theme = theme_light()) + ggtitle("Good residuals"),
                      mod$plot(mod$set_prm("include_z", TRUE)$gen(300, computed = select(dat, x, e)), theme = theme_light()) + ggtitle("Non-linearity"),
                      mod$plot(heter_model(b = 64)$gen(300, computed = select(dat, x, e)), theme = theme_light()) + ggtitle("Heteroskedasticity"),
                      mod$plot(heter_model(b = 0, e = rand_lognormal(sigma = 0.5))$gen(300, computed = select(dat, x)), theme = theme_light()) + ggtitle("Non-normality"))
```

@@

Heterskedasticity refers to the existence of nonconst error variance in a regression model. It is mostly due to the strict but false assumptions on the variance-covariance matrix of the error term. The usual pattern of heterskedasticity on a residual plot is the inconsistent spread of the residuals at different x values. Visually, it sometimes results in the so-called "butterfly" shape as shown in the bottom-left panel of Figure [ref here], or the "left-triangle" and "right-triganle" shape where the smallest variance occurs at the edges of the x-axis.

@@

@@

-   Very briefly explain what a lineup test is
-   Lineup (maybe using your previous residual plot for nonlinearity)
-   $p$-value calulcation, briefly, including how multiple selections are handled
-   power calculation, briefly, including how multiple selections are handled

However, unlike hypothesis testing built upon rigorous statistical procedures, reading diagnostic plots relies on graphical perception - human's ability to interpret and decode the information embedded in the graph [@cleveland_graphical_1984], which is to some extent subjective and indecisive. Further, visual discovery suffers from its unsecured and unconfirmed nature where the degree of the presence of the visual features typically can not be measured quantitatively and objectively, which may lead to over or under-interpretations of the data. One such example is finding an over-interpretation of the separation between gene groups in a two-dimensional projection from a linear discriminant analysis when in fact there are no differences in the expression levels between the gene groups and separation is not an uncommon occurrence [@roy_chowdhury_using_2015].

>>>>

```{r}

set.seed(10086)

mod <- poly_model(include_z = FALSE, sigma = 0.25)
dat <- mod$gen(300)
patchwork::wrap_plots(mod$plot(dat, theme = theme_light()) + ggtitle("Good residuals"),
                      mod$plot(mod$set_prm("include_z", TRUE)$gen(300, computed = select(dat, x, e)), theme = theme_light()) + ggtitle("Non-linearity"),
                      mod$plot(heter_model(b = 64)$gen(300, computed = select(dat, x, e)), theme = theme_light()) + ggtitle("Heteroskedasticity"),
                      mod$plot(heter_model(b = 0, e = rand_lognormal(sigma = 0.5))$gen(300, computed = select(dat, x)), theme = theme_light()) + ggtitle("Non-normality"))
```

@@

Heterskedasticity refers to the presence of nonconst error variance in a regression model. It is mostly due to the strict but false assumptions on the variance-covariance matrix of the error term. The usual pattern of heterskedasticity on a residual plot is the inconsistent spread of the residuals at different x values. Visually, it sometimes results in the so-called "butterfly" shape as shown in the bottom-left panel of Figure [ref here], or the "left-triangle" and "right-triganle" shape where the smallest variance occurs at the edges of the x-axis.

@@

Other than checking diagnostic plots, analysts may perform formal hypothesis testing for detecting model defects. Depending on the alternative hypothesis that is focused on, a variety of tests can be applied. For example, the presence of heteroskedasticity can usually be tested by applying the White test [\@white_heteroskedasticity-consistent_1980] or the Breusch-Pagan test [\@breusch_simple_1979], which are both derived from the Lagrange multiplier test [\@silvey1959lagrangian] principle that relies on the asymptotic properties of the null distribution. For testing non-linearity, one may apply the F-test to examine the significance of specific polynomial and non-linear forms of the regressors, or the significance of proxy variables as in the Ramsey Regression Equation Specification Error Test (RESET) [\@ramsey_tests_1969]. And for testing normality, the shapiro--Wilk test [ref here] is perhaps the most widely used test reported by many of the statistical softwares. Another choice will be the Jarque--Bera test [ref here] which directly checks if the sample skewness and kurtosis match a normal distribution.

```{r}

set.seed(10086)

mod <- poly_model(include_z = FALSE, sigma = 0.25)
dat <- mod$gen(300)
patchwork::wrap_plots(mod$plot(dat, theme = theme_light()) + ggtitle("Good residuals"),
                      mod$plot(mod$
                                 set_prm("include_z", TRUE)$
                                 gen(300, computed = select(dat, x, e)), theme = theme_light()) + 
                        ggtitle(paste("F-test p-value =", 
                                      mod$
                                        test(mod$
                                               gen(300, computed = select(dat, x, e)))$p_value %>% 
                                        format(digits = 2))),
                      mod$
                        plot(heter_model(b = 64)$
                               gen(300, computed = select(dat, x, e)), theme = theme_light()) + 
                        ggtitle(paste("BP test p-value =", 
                                      HETER_MODEL$
                                        test(heter_model(b = 64)$
                                               gen(300, computed = select(dat, x, e)))$p_value %>% 
                                        format(digits = 2))),
                      mod$
                        plot(heter_model(b = 0, e = rand_lognormal(sigma = 0.5))$
                               gen(300, computed = select(dat, x)), theme = theme_light()) + 
                        ggtitle(paste("Non-normality", 
                                      shapiro.test(heter_model(b = 0, e = rand_lognormal(sigma = 0.5))$
                                                     gen(300, computed = select(dat, x))$.resid)[[2]] %>% 
                                        format(digits = 2))))

@@

Unlike hypothesis testing built upon rigorous statistical procedures, reading diagnostic plots relies on graphical perception - human's ability to interpret and decode the information embedded in the graph [\@cleveland_graphical_1984], which is to some extent subjective and indecisive. Further, visual discovery suffers from its unsecured and unconfirmed nature where the degree of the presence of the visual features typically can not be measured quantitatively and objectively, which may lead to over or under-interpretations of the data. One such example is finding an over-interpretation of the separation between gene groups in a two-dimensional projection from a linear discriminant analysis when in fact there are no differences in the expression levels between the gene groups and separation is not an uncommon occurrence [\@roy_chowdhury_using_2015].

-   Very briefly explain what a lineup test is

-   Lineup (maybe using your previous residual plot for nonlinearity)

-   $p$-value calulcation, briefly, including how multiple selections are handled

-   power calculation, briefly, including how multiple selections are handled

### 2022-09-06 paper_comparison/paper_comparison/paper_comparison.tex
update hypothesis testing

Heterskedasticity refers to the existence of nonconst error variance in
a regression model. It is mostly due to the strict but false assumptions
on the variance-covariance matrix of the error term. The usual pattern
of heterskedasticity on a residual plot is the inconsistent spread of
the residuals at different x values. Visually, it sometimes results in
the so-called ``butterfly'' shape as shown in the bottom-left panel of
Figure {[}ref here{]}, or the ``left-triangle'' and ``right-triganle''
shape where the smallest variance occurs at the edges of the x-axis.

@@

@@

\begin{itemize}
\tightlist
\item
  Very briefly explain what a lineup test is
\item
  Lineup (maybe using your previous residual plot for nonlinearity)
\item
  \(p\)-value calulcation, briefly, including how multiple selections
  are handled
\item
  power calculation, briefly, including how multiple selections are
  handled
\end{itemize}

However, unlike hypothesis testing built upon rigorous statistical
procedures, reading diagnostic plots relies on graphical perception -
human's ability to interpret and decode the information embedded in the
graph \citep{cleveland_graphical_1984}, which is to some extent
subjective and indecisive. Further, visual discovery suffers from its
unsecured and unconfirmed nature where the degree of the presence of the
visual features typically can not be measured quantitatively and
objectively, which may lead to over or under-interpretations of the
data. One such example is finding an over-interpretation of the
separation between gene groups in a two-dimensional projection from a
linear discriminant analysis when in fact there are no differences in
the expression levels between the gene groups and separation is not an
uncommon occurrence \citep{roy_chowdhury_using_2015}.

@@

\includegraphics{paper_comparison_files/figure-latex/unnamed-chunk-13-1.pdf}

@@

\includegraphics{paper_comparison_files/figure-latex/unnamed-chunk-16-1.pdf}

@@

>>>>

Heterskedasticity refers to the presence of nonconst error variance in a
regression model. It is mostly due to the strict but false assumptions
on the variance-covariance matrix of the error term. The usual pattern
of heterskedasticity on a residual plot is the inconsistent spread of
the residuals at different x values. Visually, it sometimes results in
the so-called ``butterfly'' shape as shown in the bottom-left panel of
Figure {[}ref here{]}, or the ``left-triangle'' and ``right-triganle''
shape where the smallest variance occurs at the edges of the x-axis.

@@

Other than checking diagnostic plots, analysts may perform formal
hypothesis testing for detecting model defects. Depending on the
alternative hypothesis that is focused on, a variety of tests can be
applied. For example, the presence of heteroskedasticity can usually be
tested by applying the White test
{[}@white\_heteroskedasticity-consistent\_1980{]} or the Breusch-Pagan
test {[}@breusch\_simple\_1979{]}, which are both derived from the
Lagrange multiplier test {[}@silvey1959lagrangian{]} principle that
relies on the asymptotic properties of the null distribution. For
testing non-linearity, one may apply the F-test to examine the
significance of specific polynomial and non-linear forms of the
regressors, or the significance of proxy variables as in the Ramsey
Regression Equation Specification Error Test (RESET)
{[}@ramsey\_tests\_1969{]}. And for testing normality, the shapiro--Wilk
test {[}ref here{]} is perhaps the most widely used test reported by
many of the statistical softwares. Another choice will be the
Jarque--Bera test {[}ref here{]} which directly checks if the sample
skewness and kurtosis match a normal distribution.

\includegraphics{paper_comparison_files/figure-latex/unnamed-chunk-7-1.pdf}

@@

Unlike hypothesis testing built upon rigorous statistical procedures,
reading diagnostic plots relies on graphical perception - human's
ability to interpret and decode the information embedded in the graph
{[}@cleveland\_graphical\_1984{]}, which is to some extent subjective
and indecisive. Further, visual discovery suffers from its unsecured and
unconfirmed nature where the degree of the presence of the visual
features typically can not be measured quantitatively and objectively,
which may lead to over or under-interpretations of the data. One such
example is finding an over-interpretation of the separation between gene
groups in a two-dimensional projection from a linear discriminant
analysis when in fact there are no differences in the expression levels
between the gene groups and separation is not an uncommon occurrence
{[}@roy\_chowdhury\_using\_2015{]}.

\begin{itemize}
\item
  Very briefly explain what a lineup test is
\item
  Lineup (maybe using your previous residual plot for nonlinearity)
\item
  \(p\)-value calulcation, briefly, including how multiple selections
  are handled
\item
  power calculation, briefly, including how multiple selections are
  handled
\end{itemize}

@@

\includegraphics{paper_comparison_files/figure-latex/unnamed-chunk-14-1.pdf}

@@

@@

\includegraphics{paper_comparison_files/figure-latex/unnamed-chunk-21-1.pdf}
